---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# `bigdpclust`

<!-- badges: start -->
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/bigdpclust)](https://cran.r-project.org/package=bigdpclust)
[![Travis-CI Build Status](https://travis-ci.org/borishejblum/bigdpclust.svg?branch=master)](https://travis-ci.org/borishejblum/bigdpclust)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/borishejblum/bigdpclust?branch=master&svg=true)](https://ci.appveyor.com/project/borishejblum/bigdpclust)
[![Downloads](https://cranlogs.r-pkg.org/badges/bigdpclust?color=blue)](https://www.r-pkg.org/pkg/bigdpclust)
<!-- badges: end -->

`bigdpclust` performs clustering of tall data using a Bayesian nonparametric Gaussian Dirichlet process mixture model.

## Installation

You can install the development version of `bigdpclust` from [GitHub](https://github.com/bigdpclust) with:

```{r GitHub-install, eval=FALSE}
#install.packages("devtools")
devtools::install_github("borishejblum/bigdpclust")
```

`bigdpclust` depends on the weightedobs branch from the `NPflow` package, which can be installed through the following command:

```{r, eval=FALSE}
devtools::install_github(repo = "borishejblum/NPflow", ref = "weightedobs")
```



```{r, message=FALSE, dev='jpeg'}
library(ggplot2)
library(bigdpclust)

n1 <- 50000
n2 <- 500
mydata <- rbind(cbind(rnorm(n1), rnorm(n = n1)),
                cbind(rnorm(n2, m=10), rnorm(n = n2, m=10)))
plot(mydata)

res <- bigdpclust(mydata, nclumps=200, 
                  Nmcmc = 2000, plotevery = 2000, burnin = 1000)
table(res$cluster[1:n1])
table(res$cluster[n1 + 1:n2])
```

-- Boris Hejblum & Paul Kirk
